\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{6}

### 2015-09-10 ICRA2016/bandits_docs/includes/abstract.tex
Added many new figures as well as updated text. Quite a bit closer

\begin{abstract}
\TODO{Fill in after rest of paper done.}
\end{abstract}

>>>>

\begin{abstract}
Recent advances in distributed computing and machine learning combined with very large datasets of images and human speech have produced a series of results that surpass decades of research in analytic methods and, in some cases, human ability.
This raises the question: can Big Data and Cloud computation produce analogous advances in robot grasping and manipulation?
We develop a Multi-Armed Bandit algorithm with correlated rewards and show that learning from a large dataset of prior grasps and 3D object models can reduce the number of samples needed for robust grasp planning using our algorithm.
To study scaling effects, we introduce the Dexterity Network (Dex-Net) 1.0, a dataset of approximately 10,000 unique 3D object models. Each object is labelled with up to 250 parallel-jaw grasps and the probability of force closure of each under uncertainty in object pose, gripper pose, and friction coefficient.
We use multi-view Convolutional Neural Networks (MV-CNNs), a new deep learning method for 3D object classification, to learn a similarity metric between 3D objects and we apply it to indexing similar objects for grasp planning at scale.
We implement our algorithm and database using the Google Cloud Platform.
Experiments on a set of 20 test objects suggest that the time taken to plan a robust grasp is approximately $3.5\times$ faster than Thompson sampling without prior data on average
Experiments on sensitivity suggest that convergence rate is fastest for objects for which the MV-CNN returns geometrically similar neighbors from Dex-Net.%, and that the convergence rate can descrease if the similarity metric measures false correlations between grasps.
Code, data, and additional information can be found at: \TODO{Url}
\end{abstract}

### 2015-09-10 ICRA2016/bandits_docs/includes/algorithm.tex
Added many new figures as well as updated text. Quite a bit closer

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
Our algorithm, detailed in Algorithm~\ref{alg:full}, plans a sequence of grasps with high $P_F$ for a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards and priors from the grasp and 3D object data in Dex-Net.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimated of the grasp with the heighest estimated $P_F$.

@@

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs) to model correlations between the $P_F$ between grasps on different objects to utilize prior grasp and object data from Dex-Net 1.0.
CCBPS were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar.

Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as an occurence of force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ on object $\mO$ from samples of object pose, gripper pose, and friction, as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is the Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
We measure similarity as a function of the euclidean distance between the output of a set of $N_f$ feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$, where $d_m$ is the dimension of the feature space.
Details on our feature maps are given in \secref{features} below.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.

@@

\noindent Intuitively, this allows observations of one grasp to constitute fractional observations of similar grasps.

\subsection{Feature Representation}
\seclabel{features}
\TODO{Move elsewhere / condense? Its a lot of information coming out of nowhere}
We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.

\subsubsection{Grasp Parameters}
\seclabel{param-features}
Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx$ is the grasp center, $\bv$ is the grasp approach, and $\rho_i$ is the $i$-th moment arms.
The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).

@@

\subsubsection{Global Object Similarity}
\seclabel{global-sim}
While force closure is based on local surface properties of an object around contact points, measuring global similarity may be similarity may be useful because the heightmaps may not capture all possible contact points for a grasp under perturbations in object and gripper pose.
Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.

>>>>

\section{Correlated Multi-Armed Bandit Algorithm}
\seclabel{algorithm}
Our algorithm, detailed in Algorithm~\ref{alg:full}, plans a sequence of grasps with high $P_F$ for a new object $\mO$ using Multi-Armed Bandits (MABs) with correlated rewards and priors from the grasp and 3D object data in Dex-Net.
We first generate a set of candidate grasps $\Gamma$ for object $\mO$ using the antipodal grasp sampling described in \secref{grasp-sampling} and predict a prior distribution for each grasp using the Dex-Net database $\mD$.
Next, we run MAB by selecting the next grasp to sample using Thompson sampling~\cite{laskey2015bandits}, sampling from our uncertainty random variables, determining force closure for the grasp on the sampled variables as described in \secref{quality}, and updating a belief distribution on the probability of force closure for each grasp.
Finally, we return the grasp for which the belief distribution has the maximum lower confidence bound, a conservative estimate of the grasp with the highest estimated $P_F$.

@@

\subsection{Predicting Grasp Quality Using Prior Data}
\seclabel{ccbps}
We use Continuous Correlated Beta Processes (CCBPs) to model correlations between the $P_F$ between grasps on different objects to utilize prior grasp and object data from Dex-Net 1.0.
CCBPS were independently proposed by Goetschalckx et al.~\cite{goetschalckx2011continuous} and Montesano and Lopes~\cite{montesano2012active} to model correlations between the Bernoulli random variables in a Beta-Bernoulli process.
Such correlations may exist when the Bernoulli random variables depend on common latent factors.
For example, two grasps may have similar $P_F$ when they contact the same shape in similar locations or the surface geometry at the contact points is similar, as evidenced by Lipschitz bounds on grasp WS metrics~\cite{pokorny2013c}.

Let $\mO$ denote the input object to Algorithm~\ref{alg:full}, and let $\Gamma$ be the set of $N_g$ candidate grasps generated for $\mO$.
We define $F_{j} = F(\bg_{j}) \in \{0, 1\}$ as force closure on an evaluation of any grasp $\bg_{j} \in \Gamma$ from samples of object pose, gripper pose, and friction as described in \secref{quality}.
Under our model, $F_j$ is a Bernoulli random variable with probability of success $\theta_{j}= P_F(\bg_{j})$.
Since $\theta_j$ is unknown, our algorithm maintains a posterior belief distribution for each $\theta_j$ based on the outcome of past force closure evaluations.
In CCBPs, the belief distribution on the Bernoulli parameter $\theta_{i,k}$ is a Beta distribution, which is specified by shape parameters $\alpha > 0$ and $\beta > 0$:

@@

A CCBP estimates the shape parameters for a grasp-object pair $\mY_{j} = (\bg_{j}, \mO_{i}) \in \mM$ using a normalized kernel function $k(\mY_p, \mY_q) : \mM \times \mM \rightarrow [0,1]$ that measures similarity between a pair of grasps and objects from the Grasp Moduli Space $\mM$.
The kernel approaches 1 as the arguments become increasingly similar and approaches 0 as the arguments become dissimilar.
We measure similarity as a function of the euclidean distance between the output of a set of $N_f$ feature maps $\phi_m: \mM \rightarrow \mathbb{R}^{d_m}$ for $m = 1, ..., N_f$, where $d_m$ is the dimension of the feature space.
Details on our feature maps are given in \secref{features} below.
Given the feature maps, we use the squared exponential kernel 
\begin{align*}
	k(\mY_p, \mY_q) &= \exp\left( - \frac{1}{2} \sum \limits_{m=1}^{N_f} \|\phi_m(\mY_p) - \phi_m(\mY_q)\|_{C_m}^2 \right).
\end{align*}
\noindent where $C_m \in \bR^{d_m \times d_m}$ is the bandwidth for $\phi_m$ and $\| \by \|_{C_m} = \by^T (C_m^T C_m)^{-1} \by$.
The bandwidths are hyperparameters of the algorithm that might be set by cross-validation on a set of training data~\cite{rasmussen2006}.

@@

\noindent Intuitively, this allows evaluations of a grasp on an object to constitute fractional evaluations of similar grasps on similar objects.

\subsection{Feature Representation}
\seclabel{features}
\TODO{Condense section / possibly move earlier.}
We feature maps based on the grasp parameters $\phi_g$, the object local surface geometry $\phi_h$, and the global object shape $\phi_s$ to capture correlations between the $P_F$ of grasps.

\subsubsection{Grasp Parameters}
\seclabel{param-features}
Our first feature map is $\phi_{g}(\mY) = (\bx, \bv, \| \rho_1 \|_2, \| \rho_2 \|_2)$ where $\bx \in bR^3$ is the grasp center, $\bv \in \bS^2$ is the grasp approach, and $\rho_i \in \bR^3$ is the $i$-th moment arm.
The moment arms are included because points on the object surface with larger moment arms will move greater distances under object orientation uncertainty.
However, similarity $\phi_g$ may not indicate similar $P_F$ if the surfaces near the contact locations are dissimilar (consider two grasps that contact a box near the corner).

@@

\subsubsection{Shape Features}
\seclabel{global-sim}
While force closure is based on local surface properties of an object around contact points, measuring global similarity may be useful because the heightmap gradients may not capture all possible contact locations for a grasp under perturbations in object and gripper pose.
Thus we also use the feature map $\phi_{s}(\mY) = \psi(\mO)$, where $\psi$ is the similarity embedding based on MV-CNNs described in \secref{object-similarity}.

### 2015-09-10 ICRA2016/bandits_docs/includes/conclusion.tex
Added many new figures as well as updated text. Quite a bit closer

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies using supervision, with the goal of a future system that maps directly from images to motor torques.

Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
This presents a challenge because the number of labels per object and grasp may be smaller thatnwith probability of force closure due to the time cost involved.
Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We will also add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}.
To achieve this we will work toward releasing Dex-Net as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

>>>>

One current shortcoming of our method is that it relies on a set of features manually designed to predict grasp quality for a grasp and object, such as heightmaps and CNNs that predict object category.
Future work will leverage recent developments in feature learning with Deep Neural Networks~\cite{krizhevsky2012imagenet} to optimize grasp and object representations directly based on the outcome of grasp evaluations from bandit algorithms.
We are also interested in a future pipelined approach that integrates research on deep learning to predict object identity and pose directly from depth images as input to Dex-Net~\cite{guptaCVPR15a} and deep learning for control policies to map planned grasps on objects to motor torques~\cite{levine2015end}. 
We will use supervision from the data in Dex-Net to study extensions of our MV-CNNs to predict 3D object model and pose from simulated depth images of objects on a planar work surface to research deep learning approaches that map from 3D objects directly to grasp or manipulation policies, with the goal of a future system that maps directly from images to motor torques.

Future work will also add additional grasp and object data to Dex-Net, such as task constraints, the outcomes of physical trials, or human annotations.
%This presents a challenge because the number of labels per object and grasp may be smaller that with probability of force closure due to the time cost involved.
%Thus we will study using functional map networks to establish consistent maps between objects to share sparse labels throughout Dex-Net~\cite{huang2013fine}.
We plan to add additional analytic grasp metrics to Dex-Net, such as cages~\cite{diankov2010automated} or the expected Ferrari-Canny quality~\cite{kim2012physically}, and study the selection of a set of grasps that ``cover" an object surface to increase the chances that a grasp is reachable in cluttered environments.
We plan to release Dex-Net in the future as an open-access project with an open-source API for labelling objects in the Cloud with analytic quality metrics or simulation outcomes and integrating Dex-Net with physical robots.

### 2015-09-10 ICRA2016/bandits_docs/includes/dataset.tex
Added many new figures as well as updated text. Quite a bit closer

\TODO{Make this flow with above paragraph!}
The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
\figref{datasets} details the data sources and their sizes.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present).}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

@@

\subsection{Object Similarity Embedding}
\seclabel{object-similarity}
In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape retrieval that uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.

@@

%In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
%The image classification training step had a test accuracy of 76\%.

>>>>

\TODO{Perhaps a cleaner transition here}
The Dexterity Network (Dex-Net) 1.0, is a dataset of prior 3D object models annotated with parallel-jaw grasps and a similarity metric to efficiently index objects.
Dex-Net consists of over 10,000 3D mesh models, selected to represent objects that might be encountered in warehousing or the home such as tableware, tools, and toys.
%Laser-scanned models from the KIT object database~\cite{kasper2012kit}, the Amazon Picking Challenge objects, BigBIRD~\cite{singh2014bigbird}, and YCB ~\cite{calli2015benchmarking} constitute 355 of the total models.
%The majority of Dex-Net is synthetic 3D mesh models from 3DNet\cite{wohlkinger20123dnet}, a benchmark for object detection in robotics research,  ModelNet~\cite{wu20143d}, a benchmark for 3D model classification, and the SHREC 2014 large scale object retrieval challenge~\cite{li2015comparison}, a competition benchmark with many categories to test the state-of-the-art in shape retrieval annually.
\figref{datasets} details the data sources and their sizes.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.1]{figures/dataset_table.jpg}
\caption{The seven datasets used in Dex-Net 1.0 with information on whether or not the models were laser-scanned, the number of models in the dataset, and the number of labelled categories (if category labels are present). \TODO{Remove columns}}
\figlabel{datasets}
\vspace*{-15pt}
\end{figure}

@@

\subsection{Object Similarity Embedding}
\seclabel{object-similarity}
In order to efficiently index prior 3D object and grasp data from Dex-Net, we embed each object in a Euclidean feature space in which similar objects are close together.
Our similarity embedding is based on multi-view Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a new method for 3D shape classifciation that outperforms previous methods and uses the powerful features leared by CNNs on millions of images~\cite{krizhevsky2012imagenet}.

@@

In our implementation, we trained our MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison} for 500,000 iterations of SGD, and the final PCA step captured approximately 85\% of the variance of the vectors.
The image classification training step had a test accuracy of 76\%.
To validate that our implementation was working, we tested our method on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% for the winner of the challenge~\cite{li2015comparison}.
